Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-22 paper.qmd
Updated Figure 14 a1, b1

trimesh_removed_pbmc <- ggplot() + 
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = umap_pbmc_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  coord_fixed() +
  interior_annotation("a1") +
  theme(
    aspect.ratio = 1
  )

@@

trimesh_removed_pbmc_best <- ggplot() + 
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = umap_pbmc_scaled_best,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.2,
    color = "#000000"
  )  +
  coord_fixed() +
  interior_annotation("b1") +
  theme(
    aspect.ratio = 1
  )

>>>>

trimesh_removed_pbmc <- ggplot() + 
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c",
               linewidth = 1) +
  geom_point(
    data = umap_pbmc_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.1,
    color = "#000000"
  )  +
  interior_annotation("a1") +
  theme(
    aspect.ratio = 1
  )

@@

trimesh_removed_pbmc_best <- ggplot() + 
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c",
               linewidth = 1) +
  geom_point(
    data = umap_pbmc_scaled_best,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.2,
    color = "#000000"
  )  +
  interior_annotation("b1") +
  theme(
    aspect.ratio = 1
  )
